\section{Appendix A - List of Resources}

\subsection{Summary of Program}

\begin{itemize}
\item
\ul{FSA Statement on Capital Approach Utilised in UK Bank Recapitalisation Package}, Financial Services Authority, November 14, 2008 -- \emph{FSA press release providing its initial -- and less detailed -- description of the stress test.} \url{http://webarchive.nationalarchives.gov.uk/20091212045501/http://www.fsa.gov.uk/pages/Library/Communication/Statements/2008/capapp.shtml}
\item
\ul{FSA statement on its use of stress tests}, Financial Services Authority, May 28, 2009 -- \emph{FSA press release providing its most detailed description of the stress test.} \url{http://www.fsa.gov.uk/pages/Library/Communication/PR/2009/068.shtml}
\end{itemize}

\subsection{Implementation Documents}
\begin{itemize}
\item
\ul{Dunfermline Building Society Property Transfer Instrument 2009 }, Bank of England, March 30, 2009 -- \emph{Term sheet for the Dunfermline transaction in accordance with the ``Special Resolution Regime'' from the 2009 Banking Act.} \url{http://www.bankofengland.co.uk/financialstability/Documents/role/risk_reduction/srr/resolutions/dunfermlinecombinedtransferinstrument.pdf}
\end{itemize}

\subsection{Legal/Regulatory Guidance}

\begin{itemize}
\item
\ul{2009 Banking Act}, Parliament, February 2009 -- \emph{Act of Parliament authorizing the FSA, HM Treasury and Bank of England to use the ``Special Resolution Regime.''} \url{http://www.legislation.gov.uk/ukpga/2009/1/introduction}
\end{itemize}

\subsection{Press Releases/Announcements}

\begin{itemize}
\item
\ul{Financial support to the banking industry}, HM Treasury, October 8, 2009 -- \emph{Press release which
 announces the UK's major response to the banking crisis.} \url{http://webarchive.nationalarchives.gov.uk/20090224112406/http://www.hm-treasury.gov.uk/press_100_08.htm}
\item
\ul{FSA Statement on Capital Approach Utilised in UK Bank Recapitalisation Package}, Financial Services Authority, November 14, 2008 -- \emph{FSA press release providing its initial -- and less detailed -- description of the stress test.} \url{http://webarchive.nationalarchives.gov.uk/20091212045501/http://www.fsa.gov.uk/pages/Library/Communication/Statements/2008/capapp.shtml}
\item
\ul{FSA Statement on regulatory approach to bank capital}, Financial Services Authority, January 19, 2009-- \emph{Press release
 providing additional details on the FSA stress test and hurdle rates.} \url{http://webarchive.nationalarchives.gov.uk/20091212045501/http://www.fsa.gov.uk/pages/Library/Communication/Statements/2009/bank_capital_.shtml}
\item
\ul{FSA statement on its use of stress tests}, Financial Services Authority, May 28, 2009 -- \emph{FSA press release providing its most detailed description of the stress test.} \url{http://www.fsa.gov.uk/pages/Library/Communication/PR/2009/068.shtml}
\end{itemize}

\subsection{Media Stories}

\begin{itemize}
\item
\ul{Barclays a step closer to passing stress test}, Jane Croft, Financial Times, March 26, 2009 -- \emph{Article providing details on the timing of Barclays' stress test and its likelihood of passing.} \url{http://www.ft.com/intl/cms/s/0/76fedcf8-1a47-11de-9f91-0000779fd2ac.html}
\item
\ul{Barclays}, Lex, Financial Times, March 27, 2009 -- \emph{Article announcing that Barclays had passed the stress test.} \url{http://www.ft.com/intl/cms/s/3/d170d4fe-1adb-11de-8aa3-0000779fd2ac.html}
\item
\ul{HM Treasury refuses FOI stress test data}, Paul Murphy, Financial Times, May 22, 2009 -- \emph{Article describing the low level of disclosure around the FSA's stress tests and HM Treasury's rejection of Freedom of Information requests about the tests.} \url{http://www.ft.com/intl/cms/s/3/d170d4fe-1adb-11de-8aa3-0000779fd2ac.html}
\item
\ul{FSA releases ‘not-so-stressy’-test methodology}, Isabella Kaminska, Financial Times, May 28, 2009 -- \emph{Article describing the scenarios used in the FSA's stress tests.} \url{http://ftalphaville.ft.com/2009/05/28/56325/fsa-releases-not-so-stressy-test-methodology/}
\end{itemize}

\subsection{Key Academic Papers}

\begin{itemize}
\item
\ul{Why Banks Failed the Stress Test},
 Andrew G. Haldane, February 10, 2009 -- \emph{Speech identifying the problems with routine stress tests and proposals to fix them.} \url{http://www.bis.org/review/r090219d.pdf}
\end{itemize}

\subsection{Reports/Assessments}

\begin{itemize}
\item
\ul{UK: The Banking Act 2009},
Andrew McKnight, June 8, 2009-- \emph{Report discussing the impact of the 2009 Banking Act.} \url{http://www.mondaq.com/x/80880/Credit+Crisis+Emergency+Economic+Stabilization+Act/The+Banking+Act+2009}
\item
\ul{FSA Annual Report}, Financial Services Authority, June 2010 -- \emph{FSA annual report discussing the stress test conducted during the crisis and the impacts of those tests.} \url{http://www.fsa.gov.uk/pubs/annual/ar09_10/ar09_10.pdf}
\end{itemize}
